---
title: "Ames Housing Graph"
output:
  html_document:
    fig_height: 2
    fig_width: 5
  word_document:
    fig_height: 2
    fig_width: 5
---

### My Favorite Graph

```{r message = FALSE, warning = FALSE}
# This tutorial will use the following two packages
library(ggplot2)
require(ggplot2)
library(mosaic)
```

In this tutorial, we will use the  [AmesHousing](http://www.amstat.org/publications/jse/v19n3/decock.pdf) data, which provides information on the sales of individual residential properties in Ames, Iowa from 2006 to 2010. The data set contains 2930 observations, and a large number of explanatory variables involved in assessing home values. A full description of this dataset can be found [here](http://www.amstat.org/publications/jse/v19n3/Decock/DataDocumentation.txt).

```{r}
# The csv file should be imported into rstudio:
AmesHousing <- read.csv("data/AmesHousing.csv")
AmesHousing <- mutate(AmesHousing, TotalSqFt = AmesHousing$Gr.Liv.Area + AmesHousing$Total.Bsmt.SF)
AmesHousing <- filter(AmesHousing, AmesHousing$TotalSqFt < 3000)
# str(AmesHousing)
```
A

Here is my favorite graph of the Ame Housing data.

```{r}
ggplot(data = AmesHousing) +                         
  geom_point(aes(x=log(TotalSqFt), y=log(SalePrice), color=AmesHousing$Kitchen.Qual),shape=1,size=1) +
  geom_smooth(aes(x=log(TotalSqFt), y=log(SalePrice), color=AmesHousing$Kitchen.Qual), method = loess, size=1) +
  labs(title = "Predicting Ames Housing Prices")
```

**Remarks:**
Provide a short description of your work here.






